Data set Imported Here:
```{r}
sqsData <- read.csv("SQS-UserPersonalizationProcessingQueue.csv", header = TRUE, sep = ";", stringsAsFactors = TRUE)
typeof(sqsData)
str(sqsData)
```

Great. now you are in possession of sqs stats from grafana in the format of csv
go ahead and take a look at it

```{r}
# sqsData
```





Since you already have the imported CSV data, why not experemnt and get yourself familiar with schema:
```{r}
sqsDataMatrix <- as.matrix(sqsData)
sqsDataVector <- as.vector(sqsData)
colnames(sqsDataMatrix)
colnames(sqsDataVector)
```
Excellent, now you can go ahead and play around with data.
here is an example on sum()
```{r}
deletedMessagesSum <- sum(as.numeric(sqsData$NumberOfMessagesDeleted_Sum))
receivedMessagesSum <- sum(as.numeric(sqsData$NumberOfMessagesReceived_Sum))
sentMessagesSum <- sum(as.numeric(sqsData$NumberOfMessagesSent_Sum))

data.frame("deleted" = deletedMessagesSum, "received" = receivedMessagesSum, "sent" = sentMessagesSum)
```
since you are at it, go ahead and draw a chart from it as well.
```{r}
library(lattice)

timeList              <- as.double.difftime(sqsData$Time)
deletedMessagesList   <- as.integer(sqsData$NumberOfMessagesDeleted_Sum)
receivedMessagesList  <- as.integer(sqsData$NumberOfMessagesReceived_Sum)
sentMessagesSumList   <- as.integer(sqsData$NumberOfMessagesSent_Sum)

chartDataFrame <- data.frame("time" = timeList, "deleted" = deletedMessagesList, "received" = receivedMessagesList, "sent" = sentMessagesSumList)

xyplot(
  deletedMessagesList+receivedMessagesList+sentMessagesSumList~timeList,
  data = chartDataFrame,
  type = "l",
  auto.key=list(space='bottom')
)
```